\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data

### 2018-10-12 paper/supporting_information.tex
finished pass through supplemental figures document

\title{\textit{Supplemental Figures for}: A Gaussian process model of human electrocorticographic data} 
\author{
  Lucy L. W. Owen$^{1}$,
  Andrew C. Heusser$^{1, 2}$, and
  Jeremy R. Manning$^{1\ast}$\\\\
$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
Hanover, NH 03755, USA\\
$^{2}$Akili Interactive,\\
Boston, MA 02110, USA}

@@

\begin{figure}[b!]
\centering
\includegraphics[width=0.6\textwidth]{figs/supplemental_1}
\caption{\textbf{Reconstruction quality for datasets 1 and 2.}
  \textbf{A. Distributions of correlations between observed versus
    reconstructed activity by electrode, for Dataset 1.} The split violin
  plot reflects the same data as Figure~3A, presented here for
  comparison.  The ``\textbf{B. Distributions of correlation between
    observed versus reconstructed activity by electrode, for Dataset
    1.}  The right-most split violin plot (``All'') reflects the same data as Figure~3B,
  presented here for comparison.  The ``Within'' plot reflects the
  same analyses, but limited to models that were trained and tested on
  the same Dataset 2 experiments.  The ``Across'' plot reflects the
  same analyses, but limited to models that were trained and tested on
  \textit{different} Dataset 2 experiments.  All plots: the dark gray
  distributions denote across-subject correlations (model trained on
  all but one patient and tested on the held-out patient), and the
  light gray distributions denote within-subject correlations (model
  trained on all but one electrode from one patient, and tested on the
  held-out electrode).  The horizontal bars denote $t$-tests between
  the corresponding distributions, and the white numbers reflect the
  distribution means.  The symbols denote the corresponding $p$-values
of those statistical tests.}
\label{fig:supplemental_1}
\end{figure}

@@

\begin{figure}[ptb]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_5}
\caption{\textbf{Most informative electrode locations.}  This map
  shows the region outlined in white from Figure~5 in greater detail.
Across Datasets 1 and 2, electrodes in these locations were identified as yielding the (10\%)
best reconstruction accuracies at \textit{other} locations throughout
the brain.}
\label{fig:supplemental_5}
\end{figure}

>>>>

\title{\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data} 
\author{
  Lucy L. W. Owen$^{1}$,
  Andrew C. Heusser$^{1, 2}$, and
  Jeremy R. Manning$^{1\ast}$\\\\
$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
Hanover, NH 03755, USA\\
$^{2}$Akili Interactive,\\
Boston, MA 02110, USA}

@@

\begin{figure}[b!]
\centering
\includegraphics[width=0.6\textwidth]{figs/supplemental_1}
\caption{\textbf{Reconstruction quality for Datasets 1 and 2.}
  \textbf{A. Distributions of correlations between observed versus
    reconstructed activity by electrode, for Dataset 1.} The split
  violin plot reflects the same data as Figure~3A, presented here for
  comparison.  \textbf{B. Distributions of correlation between
    observed versus reconstructed activity by electrode, for Dataset
    2.}  The right-most split violin plot (``All'') reflects the same
  data as Figure~3B, presented here for comparison.  The ``Within''
  plot reflects the same analyses, but limited to models that were
  trained and tested on only one of the Dataset 2 experiments at a
  time.  The ``Across'' plot reflects the same analyses, but limited
  to models that were trained and tested on \textit{different} Dataset
  2 experiments.  All plots: the dark gray distributions denote
  across-subject correlations (model trained on all but one patient
  and tested on the held-out patient), and the medium gray
  distributions denote within-subject correlations (model trained on
  all but one electrode from one patient, and tested on the held-out
  electrode).  The horizontal bars denote $t$-tests between the
  corresponding distributions (after $z$-transforming the
  correlations), and the white numbers reflect the distribution means.
  The symbols denote the corresponding $p$-values of those statistical
  tests.}
\label{fig:supplemental_1}
\end{figure}

@@

\begin{figure}[ptb]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_5}
\caption{\textbf{Most informative electrode locations.}  This map
  shows the region outlined in white from Figure~5 in greater detail.
  Across Datasets 1 and 2, electrodes in these locations were
  identified as yielding the (10\%) best reconstruction accuracies at
  \textit{other} locations throughout the brain.  The $x$-coordinates
  in each panel denote the positions of the sagittal slices in MNI space.}
\label{fig:supplemental_5}
\end{figure}
